Naive Bayes Classifier

### 2019-02-25 NB_2r2c.Rmd
updates

---
title: "Naive Bayes Analysis Ver 2r.2c"
author: "Dan Johnson"
date: "2/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Summary
This it the current Naive Bayes workflow used to classify TA comments based on Subject and Structure. Additions and revisions made to **Version 2r.2c** are:

*  Random selection of data rows used for training and test datasets. 
*  Final output matrix tables are more informative. 
*  Addition of a back-analysis step that reviews entire dataset, not just testing sub-set.
*  Outputs a tidy data table in CSV format that contains the original comments (pre-clean-up) plus their hand-scored and predicted subject and structure.

>>>>

---
title: "Naive Bayes Classifier"
date: "2/24/2019"
bibliography: library.bib
biblio-style: apalike
---

```{r, child="_setup.Rmd"}
```

#Overview
This is the current version of the Naive Bayes workflow used to classify TA comments based on Subject and Structure. Features of **Version 2r.2c**:

*  Data rows used for training and test datasets are assigned randomly but reproducibly using 'set.seed'. 
*  Detailed final output matrix tables. 
*  Back-analysis evaluates both a testing sub-set and the entire input dataset.
*  Outputs a tidy data table in CSV format with unmodified original comments, and hand-scored and NB-predicted Subject and Structure assignments.

This page outlines Ver 2r.2c of NB Classifier and the process for building various components used in the project. Details of each  component are provided in these sub-pages.

For structure of the initial dataset see: https://adanieljohnson.github.io/default_website/datastructure.html

For import and post-import data validation see: https://adanieljohnson.github.io/default_website/dataimport.html
